---
title: "my_function_bootstrap"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my_function_bootstrap}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
knitr::opts_chunk$set(echo = FALSE)
# Load packages
library(Xu.Jin.4864final.package)
suppressMessages(library(dplyr))
suppressMessages(library(ggplot2))
suppressMessages(library(tidyverse))
suppressMessages(library(lme4))
suppressMessages(library(readr))
```

# 1. Brief Introduction
In this package, we create functions for fitting one of the generalized linear mixed effects models (GLMMs), the Poisson model, and implement maximum likelihood inference including computing point estimates, standard errors, and confidence intervals. 

A sample data set gopher tortoises (Ozgul et al., 2009) are used here to show how function works.

We first fit a Poisson model with tortoise data set. Then, we use then bootstrap to re-sample data to compute standard deviation and confidence interval. The goal is to test whether increasing in seroprevalence will affect survival of tortoise accounting for the area of each sites. 

This Vignette including Exploratory Data Analysis of original data set, Model Fitting Process, Bootstrap Process and Result Implication.


# 2. Exploratory Data Analysis
In this section, because the density and type value are not used in fitting model, so we clean these two columns out.
```{r echo=TRUE}
# Import the sample data set
library(readr)
tortoise <- read_csv("gopher_tortoise.csv", show_col_types = FALSE)

# Clean the date set, removed unused column
tortoise_clean <- tortoise %>%
  select("Site", "year", "shells", "Area", "prev")
```

## 2.1 Relationship between number of shells and year effect

The plot shows the relationship between shells and year in original data set, it is grouped by each site. Each site shows different tendency of shell number in these three years, some increase, while other decrease.
```{r}
# Relationship between shells and year
tortoise_clean %>%
  ggplot(aes(x = year, y = shells, fill = Site)) +
  geom_bar(stat="identity") + 
  ggtitle("Shells Frequency Plot") +
  ylab("Number of Shells") +
  facet_wrap(. ~ Site, ncol=3) +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(legend.position = "none") +
  scale_y_continuous(breaks=seq(0, 9, 2))
```

\newpages

## 2.2 Relationship between number of shells and area of each sites

This plot shows relationship between area and shell. As plot shows, increasing in the area will somehow lead to an increase in number of shells. Hence. in the model, to avoid area effects, number of shells is divided by area.

```{r}
# Relationship between shells and sites area
tortoise_clean %>%
  ggplot(aes(x = Area, y = shells)) +
  geom_line() + 
  ggtitle("Shells Frequency VS Area") +
  ylab("Number of Shells") +
  facet_wrap(. ~ year, ncol=3) +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_x_continuous(breaks=seq(0, 60, 10))
```

\newpages

## 2.3 Relationship between average number of shells and seroprevalence

The first plot compares the relationship between number of shells and seroprevalence. However, we should consider the effect bring by area of each site.

```{r}
# Relationship between shells and seroprevalance (prev)
tortoise_clean %>%
  ggplot(aes(x = prev, y = shells)) +
  geom_line() + 
  ggtitle("Shells Frequency VS prev") +
  ylab("Average Number of Shells") +
  facet_wrap(. ~ year, ncol=3) +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5))
```

The second plot compares the relationship between average number of shells and seroprevalence, where average number of shells means the number of shells divided by area. The observation here is, as seroprevalence increase, the number of shells also generally increase.

```{r}
# Divide shells by area
tortoise2 <- tortoise_clean %>%
  mutate(count_per_area = shells/Area)
```

```{r}
# Relationship between average shells and seroprevalance (prev)
tortoise2 %>%
  ggplot(aes(x = prev, y = count_per_area)) +
  geom_line() + 
  ggtitle("Average Shells Frequency VS prev") +
  ylab("Average Number of Shells") +
  facet_wrap(. ~ year, ncol=3) +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5))
```

# 3. Explanation of model fitting and bootstrap process

## 3.1 Fitting poisson model
In this part, we use the function "run_model" provided by Dr. Simon Bonner to fit a poisson model for this data set. We use number of shells as response variable, with predictors including seroprevalance, area, year and random effect bring by site.

To use this function, the first parameter is the data set, and the second means example we use. Note that this function currently only can fit with four example data sets, 2 of poisson model and 2 of binomial model.

```{r echo=TRUE, warning=FALSE}
suppressMessages(run_model(tortoise, "tortoise"))
```

Summary of model shows that this data set has no random effects with 0 random effects variance.

## 3.2 Bootstrap and refitting 

Bootstrap process is implementing by the function "para_boot". To make this function run successfully, we need three parameters. Similar to "run_model", the fit parameter is the name of data set and second is name of example. In our sample data set, the second parameter is "tortoise". The third parameter is number of bootstrap we want to run, in other word, the sample size of bootstrap.

By running this function, the result will be a table containing value of point estimation, re-sampled $\beta_1$ value, standard deviation, 95%CI and p value of $\beta_1$.

Here, we run the bootstrap function with sample size 30 as an example.
```{r echo=TRUE, warning=FALSE}
suppressMessages(para_boot(tortoise, "tortoise", 30))
```

# 4. Explanation of Summary Output
Here is the process of picking best value of B, the sample size of bootstrap. We aim to pick a proper value of B and we expect it will converge at some point. Here, we pick mean square error (MSE) to test the variation and bias.
```{r warning=FALSE}
# Avoid warning message
options(dplyr.summarise.inform = FALSE)

MSE <- data.frame(index = seq(from = 10, to = 300, by = 10)) %>%
  group_by(index) %>%
  summarize(boot_sample = suppressMessages(para_boot(tortoise, "tortoise", index))) %>%
  mutate(value = mean(boot_sample[[2]] - boot_sample[[1]])^2, .groups = "keeps")

MSE_plot <- data.frame(B = MSE$index, MSE = MSE$value) %>%
  ggplot() +
  geom_line(aes(x = B, y = MSE), linewidth = 0.8) +
  ggtitle("Plot of MSE for bootstrap samples vs different value of B") +
  theme_bw()
MSE_plot
```

From this plot, we find out after 100, the MSE value started to converge, which means that it is enough if we only keep value of B as 100. 

Now, we rerun our bootstrap function with B equal to 100.
```{r echo=TRUE, warning=FALSE}
suppressMessages(para_boot(tortoise, "tortoise", 100))
```

In this output, the first value is the point estimate of $\beta_1$ after fitting the model. This is the original value of $\beta_1$ that we obtain before doing bootstrap to refit the model. 

The second group of value is the $\beta_1^*$ we obtain after refitting model with new generated random effects. A clear observation here is, all these $\beta_1^*$ are around the original point estimate, some above it, some below it, but still value close. This phenomenon also can be viewed from very small standard error, which is the third value. It means these data do not cause value of $\beta_1$ fluctuating a lot. The forth part of output is the value of our 95% confidence interval. 

The last value is p-value of hypothesis test in bootstrap. Here we rerun the bootstrap at the condition that $\beta_1$ is equal to 0, because we need to approximate the sampling distribution under the null hypothesis, so this is different from what we compute standard error and confidence interval. This result shows that our p-value is very small, which means we have evidence to reject our null hypothesis, where null hypothesis is $H_0: \beta_1 = 0$. Since it is rejected, then we know that the impact of seroprevalance to number of shells is significant, we conclude that increasing in seroprevalance will affect number of shells.

